---
title: "p8105_hw1_yf2555"
author: Yihan Feng 
output: github_document
 
---

This is my solution to homework 1. 

```{r, warning = FALSE}
library(tidyverse)
```


# Problem 1

## 1. Create a data frame with specified elements

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```


## 2. Try to take the mean of variables
```{r, results = "hide", warning = FALSE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of "samp" and "samp_gt_0", but not "char_vec" or "factor_vec". 


```{r, results = "hide", warning = FALSE} 
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

The output shows that "samp" and "samp_gt_0" can be converted to numeric, but "char_vec" or "fector_vec" cannot. It is because that "samp" and "samp_gt_0" contain numeric values, so they can be converted; while "char_vec" and "factor_vec" do not contain numeric values, so they cannot be converted to numeric. 

Back to the previous code chunk and conclusion, since only numeric values can be calculated as mean, "samp" and "samp_gt_0", which contain numeric values, can be processed with mean function. Also, because "char_vec" and "factor_vec" do not contain numeric values, so they cannot be processed with mean function. 


## 3. convert the logical vector
```{r, warning = FALSE}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```






# Problem 2


## 1. load the dataset
```{r load_penguins}
data("penguins", package = "palmerpenguins")
```


## 2. description of the dataset

* The dataset includes 8 variables as: `r names(penguins)`. 
  * `r levels(penguins$species)` are the three species recorded in the dataset. 
  * The sex is recorded as `r levels(penguins$sex)`. 
  * The bill length ranges between `r range(penguins$bill_length_mm, na.rm = TRUE)` in millimeters; the bill depth ranges between `r range(penguins$bill_depth_mm, na.rm = TRUE)` in millimeters; the flipper length ranges between `r range(penguins$flipper_length_mm, na.rm = TRUE)` in millimeters; and body mass ranges between `r range(penguins$body_mass_g, na.rm = TRUE)` in grams. 

* The size of the dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

* The mean of flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 



## 3. scatterplot graphing and save it

```{r, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species), na.rm = TRUE) + geom_point()
ggsave("hw1_penguins_scatterplot.pdf")
```





