---
title: "p8105_hw1_yf2555"
author: Yihan Feng 
output: github_document
---

This is my solution to homework 1. 

```{r}
library(tidyverse)
```


# Problem 1
Create a data frame with specified elements
 
 
```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    fector_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```


```{r take_the_mean}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, fector_vec))
```

I can take the mean of numbers and logical, but not character or factor. 



```{r apply_as.numeric} 
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, fector_vec))
```

Numbers and logical variables can be converted to numeric, but character or factor variables cannot. Only numeric values can be calculated (like mean), which explains that I can take the mean of numbers and logical variables, but not character or factor variables. 


```{r convert_numeric_or_factor}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```



# Problem 2
```{r load_penguins}
data("penguins", package = "palmerpenguins")
```


*******the data in this dataset, including names / values of important variables

The size of the dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean of flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 






Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).
Export your first scatterplot to your project directory using ggsave


```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm), color = penguins$species, na.rm = TRUE) + geom_point()
```











